Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-12 paper/sections/implementation.tex
[ paper ] fixing some typos and text added.

In \Agda, we define a proposition formula
as an inductive type using the keyword \texttt{data} extending the
its definition in \cite{Altenkirch2015}.  
The \name{PropFormula} data type stands for propositions
as we define in section \ref{sec:preliminaries}.
We include every connective and logic constant as a constructor.
We also define the constructor for atomic propositions denoted by
\verb!Var!. This atomic expressions are represented using a natural 
number $i$ bounded by a size of the universe $n$ for those atomic 
propositions (in \Agda, we use the data type \verb!Fin! from the 
standard  library for such a purpose).

@@

\begin{example}
Using Unicode translating a proposition from a textbook to \Agda 
using the above data type is straightforward. 
\begin{verbatim}
r : PropFormula
p = Var (# 0)
q = Var (# 1)
r = Var (# 2)

>>>>

In \Agda, we define a proposition formula
as an inductive type using the keyword \texttt{data} extending the
its definition in \cite{Altenkirch2015}.
The \name{PropFormula} data type stands for propositions
as we define in section \ref{sec:preliminaries}.
We include every connective and logic constant as a constructor.
We also define the constructor for atomic propositions denoted by
\verb!Var!. These atomic expressions are represented using a natural
number $i$ bounded by a size of the universe $n$ for those atomic
propositions (in \Agda, we use the data type \verb!Fin! from the
standard  library for such a purpose).

@@

\begin{example}
\hspace*{5cm}\\[3mm]
\begin{verbatim}
r : PropFormula
p = Var (# 0)
q = Var (# 1)
r = Var (# 2)

### 2017-09-12 paper/sections/preliminaries.tex
[ paper ] fixing some typos and text added.

\textit{Propositions.}
We define the classical propositional logic as usual.
A proposition is an expression of indivisible propositional atoms
(e.g., symbols $φ₀, φ₁, \cdots$),
binary logic connectives ($∧, ∨, ⇒, ⇔)$,
propositional negation $(¬)$, and logic constants $⊥$
and $⊤$. We use the inductive definition of the set \PROP
defined in \cite{VanDalen1994} as the mechanism to produce any
propositional formula.
Then, $ϕ_i \in \PROP$ for all $i \in \mathbb{N}$.
If $(φ\ \square\ ψ)$ stands for a proposition that use a
binary connective where is the symbol $\square$; when $φ, ψ\in
\PROP$, then $(φ\ \square\ ψ) \in \PROP$.\change{rewrite this}
If $φ \in \PROP$, then $(¬ φ) \in \PROP$.
Finally, $⊥, ⊤ \in \PROP$.

\emph{Derivations.}
A derivation of $φ$ is a mechanism to obtain the conclusion $φ$ from
the application of some deduction steps. Such a deduction step has
the form of a set of propositional \emph{premises} that conclude the
result: one or more propositions. As we show in the following
figure, the premises are always above the line, and the conclusions
are below it. As a notation convention, if the name of a rule used
in the derivation step is typed using verbatim, that means, it is
available in our implementation for the \CPL (see the syntax module 
in \cite{AgdaProp}) used in the proof reconstruction latter.

>>>>

\textit{Propositions.}
We define the classical propositional logic as usual.
A proposition is an expression of indivisible propositional atoms
(e.g., symbols $φ₀, φ₁, \cdots$),
binary logic connectives ($∧, ∨, ⇒, ⇔)$,
propositional negation $(¬)$, and logic constants $⊥$
and $⊤$. We use the inductive definition of the set \PROP
presented in \cite{VanDalen1994} as the mechanism to produce any
propositional formula.
Then, $ϕ_i \in \PROP$ for all $i \in \mathbb{N}$.
If $φ, ψ\in \PROP$, then $(φ\ \square\ ψ) \in \PROP$,
where $(φ\ \square\ ψ)$ stands for a proposition that use a
binary connective in the place for the $\square$ symbol.
If $φ \in \PROP$, then $(¬ φ) \in \PROP$.
Finally, $⊥, ⊤ \in \PROP$.

\emph{Derivations.}
A derivation of $φ$ is a mechanism to obtain the conclusion $φ$ from
the application of some deduction steps. Such a deduction step has
the form of a set of propositional \emph{premises} that conclude the
result: one or more propositions. As we show in the following
figure, the premises are always above the line, the conclusions
are below it, and the name of the inference or the theorem used is
on the right the line. As a notation convention, if the name of a
rule used in the derivation step is typed using verbatim, that
means, it is available in our implementation (see for instance,
theorems in \cite{AgdaProp}) used in some derivations latter.

### 2017-09-12 paper/sections/proof-reconstruction.tex
[ paper ] fixing some typos and text added.

\begin{definition}
El rango $rank(\phi)$ de una proposition $\phi$ es definido como

@@

\max(rank(\phi_1),rank(\phi_2)) + 1
  & \phi := \phi_1\,\square\, \phi_2 \\
rank(\phi_1) + 1  & \phi := \neg \phi_1
\end{cases}
\end{equation}

\end{definition}

Then, we our final review for the function $\unshunt$ is the
function$\unshunt^{+}$ with type $PROP \to PROP$
with a structured recursion,

\begin{equation}
\unshunt^{+}(\varphi) = \unshunt^{*}(\varphi, rank(\varphi))
\end{equation}

In the following section, our task will consist of a searching
appropriate functions like $rank$ to assure the termination for transformation functions like $nnf$.

>>>>

\begin{definition}
Th rank of proposition φ denoted by $rank(\phi)$ is defined by the
following equation.

@@

\max(rank(\phi_1),rank(\phi_2)) + 1
  & \phi := \phi_1\,\square\, \phi_2 \\
rank(\phi_1) + 1  & \phi := \neg \phi_1
\end{cases}
\end{equation}
\end{definition}

The final review for $\unshunt$ function is the
$\unshunt^{+}$ function in Eq.~\ref{eq:unshunt-fixed}
with $PROP \to PROP$ type.

\begin{equation}
\label{eq:unshunt-fixed}
\unshunt^{+}(\varphi) = \unshunt^{*}(\varphi, rank(\varphi))
\end{equation}

In the following section, our task will consist of searching
appropriate functions like $rank$ to assure the termination for
transformation functions like $nnf$.
